An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-02 scagnostics.Rmd
More manual caching, now reasonably fast to compile.

```{r pipeFirstRun,fig.width=6, fig.height=7, fig.cap="Index value on tour path when scouting for high TIC index values."}
pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
ggplot(pipeTourResMelt, aes(x=t, y=value)) +
  geom_line() + 
  facet_wrap(~variable, ncol=1, scales = "free_y")
```

>>>>

```{r pipeFirstRun,fig.width=6, fig.height=7, fig.cap="Index value on tour path when scouting for high TIC index values."}
if(!file.exists("cache/pipeFirstRun.rda")){
  pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
  pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
  save(pipeTourRes, pipeTourResMelt, file = "cache/pipeFirstRun.rda")
} else {
  load("cache/pipeFirstRun.rda")
}
ggplot(pipeTourResMelt, aes(x=t, y=value)) +
  geom_line() + 
  facet_wrap(~variable, ncol=1, scales = "free_y")
```
